---
title: "Simple & Multiple Regression"
author: "N_M_Emran_Hussain"
date: "2024-11-04"
output: html_document
---
# Installing and Loading 'deplyr' and 'heplots' packages 
```{r}
# Loading the library
library(dplyr)

# Installing package and loading the library
install.packages("heplots")
library(heplots)
```

# Loading dataset and visualization of descriptive statistics of dependent and independent variables

```{r}
flixit_data <- read.table("FlixIt.dat", header=FALSE)
names(flixit_data) <- c("ID", "Hours", "Children", "Income", "History")
summary(flixit_data)
```
# Simple regression between Streaming Hours and number of Children and Calculation of Adjusted R^2

```{r}
hours_to_children <- lm(Hours~Children, data=flixit_data)
summary(hours_to_children)
etasq(hours_to_children, anova = TRUE, partial = FALSE)
```
# Simple regression between Streaming Hours and Income and Calculation of Adjusted R^2

```{r}
hours_to_income <- lm(Hours~Income, data=flixit_data)
summary(hours_to_income)
etasq(hours_to_income, anova = TRUE, partial = FALSE)
```

# Simple regression between Streaming Hours and History and Calculation of Adjusted R^2
```{r}
hours_to_history <- lm(Hours~History, data=flixit_data)
summary(hours_to_history)
etasq(hours_to_history, anova = TRUE, partial = FALSE)
```
# Mutiple regression between Streaming Hours and Income, Children and History

```{r}
hours <- lm(Hours~Children + Income + History , data=flixit_data)
summary(hours)
etasq(hours, anova = TRUE, partial = FALSE)
```

# Number of Sample
```{r}
num_rows <- nrow(flixit_data)
print(num_rows)
```
